\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-10-30 parts-grn.tex
cleanup bib, make Fig 1 more visible, reference to K equivalence
K-equivalence

@@

\todo{(LP) parameters equivalence:
if $\GRNedge{a}{+}{t}{a}$,
$K_{a,R\setminus \{a\}} = t
\equiv
K_{a,R\setminus \{a\}} = u$
for $t \leq u \leq l_a$;
$K_{a,R\cup \{a\}} = t-1
\equiv
K_{a,R\cup \{a\}} = u$
for $0 \leq u < t$.
If $\GRNedge{a}{-}{t}{a}$,
$K_{a,R\cup \{a\}} = t
\equiv
K_{a,R\cup \{a\}} = u$
for $t \leq u \leq l_a$;
$K_{a,R\setminus \{a\}} = t-1
\equiv
K_{a,R\cup \{a\}} = u$
for $0 \setminus u < t$.
- any other equivalence?}

>>>>

\begin{remark}[Parameters equivalence]
\label{rem:K-equiv}
\modLP{%
In the scope of the asychronous dynamics (\pref{def:dynamics}), one can remark
that some parameters values can be equivalent, i.e. the resulting dynamics is
the same.
It is notably the case with auto-regulations:
if $\GRNedge{a}{s}{t}{a}$,
then for any $\omega\subseteq \GRNreg{a}$,
two values $v$ and $v'$ of the parameter 
$K_{a,\omega\setminus \{a\}}$ are equivalent
if $v\geq t$ and $v'\geq t$.
Similary,
two values $v$ and $v'$ of the parameter
$K_{a,\omega\cup\{a\}}$ are equivalent 
if $v<t$ and $v'<t$.}
\end{remark}

@@
